---
title: "R Programming - Quiz 1"
author: "Dejan Pljevljakusic"
date: "Thursday, March 19, 2015"
output: html_document
---

Hereby, I have presented how I have solved the tasks in R Programming - Week 1 Quiz.

I have only presented solutions for data_file related questions (11-20)

### Question 11
In the dataset provided for this Quiz, what are the column names of the dataset?

```{r}
d1 <- read.csv(file.path("http://amapseec.org/coursera/", "hw1_data.csv")) ## Opens csv file and makes data frame 'd1'
d1 ## Prints out complete data frame d1
```

### Question 12
Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

```{r}
extract <- d1[1:2,] ## Extracts header and first two rows
extract ## Prints extracted extacted rows
```

### Question 13
How many observations (i.e. rows) are in this data frame?

```{r}
nrow(d1) ## Count number of rows in d1
```

### Question 14
Extract the last 2 rows of the data frame and print them to the console. What does the output look like?

```{r}
extract <- d1[152:153,] ## Extracts header and last two rows
extract ## Prints extracted extracted rows
```

### Question 15
What is the value of Ozone in the 47th row?

```{r}
extract <- d1[47,] ## Extracts header and 47 row
extract ## Prints extracted extracted rows
```

### Question 16
How many missing values are in the Ozone column of this data frame?

```{r}
bad <- is.na(d1$Ozone) ## Creates logical vector 'bad' of NA values in column 'Ozone'
sum(bad) ## Counts TRUEs in logical vector 'bad'
```

### Question 17
What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

```{r}
real <- d1$Ozone[!bad] ## Creates subset of vector in column Ozone where NA is FALSE
real ## Prints new vector
mean(real) ## Gets mean of new vector
```

### Question 18
Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

```{r}
d2 <- subset(d1, Ozone > 31 & Temp > 90) ## Creates subset of d1 for selected conditions
d2 ## Prints out new data frame 
mean(d2$Solar.R) ## Gets mean of column Solar.R
```

### Question 19
What is the mean of "Temp" when "Month" is equal to 6? 

```{r}
d3 <- subset(d1, Month == 6) ## Creates subset of d1 for selected condition
d3
mean(d3$Temp) ## Gets mean of coulumn Temp
```

### Question 20
What was the maximum ozone value in the month of May (i.e. Month = 5)?

```{r}
d4 <- subset(d1, Month == 5) ## Creates subset of d1 for selected condition
d4 ## Prints out new data frame
bad2 <- is.na(d4$Ozone) ## Creates logical vector 'bad' of NA values in column 'Ozone'
d5 <- d4$Ozone[!bad2] ## Creates subset of vector in column Ozone where NA is FALSE 
d5 ## Prints out new vector
max(d5) ## Gets maximum of new vector
```









